Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2023-02-23 thirdPaper/draft/typeConeAssociahedra.tex
Mise à jour affiliation

\author{Pierre-Guy Plamondon}
\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques de Versailles, UVSQ, CNRS, Universit\'e Paris-Saclay, Versailles}
\email{pierre-guy.plamondon@uvsq.fr}
\urladdr{\url{https://www.imo.universite-paris-saclay.fr/~plamondon/}}

>>>>

\author{Pierre-Guy Plamondon}
\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques de Versailles, UVSQ, CNRS, Universit\'e Paris-Saclay, Institut Universitaire de France (IUF)}
\email{pierre-guy.plamondon@uvsq.fr}
\urladdr{\url{https://lmv.math.cnrs.fr/laboratoire/annuaire/membres-du-laboratoire/pierre-guy-plamondon/}}
